Qubit tests from classical codes

### 2023-02-27 quantum_codes_test.tex
responded to comments

When we write $\Es{i\in \mX}$ where $\mX$ is a finite set, we mean the expectation over $i$ chosen uniformly at random from $\mX$, i.e.\ $\frac{1}{|\mX|} \sum_{i\in \mX}$.

@@

We end with a couple lemma that will prove useful. 
\hnote{there are two algebras $\mM$ and $\mN$ but the trace and identities don't specify which. we should probably write a sentence saying that it's implicit but determined by context...(if we do this, then the superscripts in the previous lemma are not needed)}

@@

\begin{definition}[Synchronous strategy]
If $G=(\mX,\mu,\mA,D)$ is a game and $(\mM,\tau)$ a tracial von Neumann algebra, a \emph{synchronous strategy $\strategy$ for $G$ on $(\mM,\tau)$} is, for every $x\in \mX$, a projective measurement $(P^x_a)_{a\in \mA(x)}$ on $\mM$. The value of a strategy $\strategy$ in $G$ is 
\[ \omega(G;\strategy)\,=\, \sum_{(x,y)\in\mX\times\mX}\frac{1}{2}\big(\mu(x,y)+\mu(y,x)\big) \sum_{(a,b)\in\mA(x)\times\mA(y)} D(x,y,a,b)\, \tau\big(P^x_a \,P^y_b\big) \;.\footnote{Note the symmetrization of $\mu$. This is to avoid explicitly requiring $\mu$ to be permutation-invariant in the definition of a game. \hnote{Didn't quite understand... what would go wrong without this symmetrization?}\tnote{It's so that at some point we can claim that studying synchronous strategies is wlog. Maybe that point happens only outside this note though; so then we can say it's to keep with the formalism of synchronous games} \hnote{sorry, still don't understand... I thought synchronous games just require that $D(x,x,a,b) = 0$ if $a \neq b$. That doesn't have anything to do with whether the distribution is symmetrized, right?}\tnote{You're right, usually they don't have a distribution because it's all about the exact case. It's still convenient though, to define games without explicitly flipping the ``symmetry'' coin. Can we keep it and simply write ``Note the symmetrization of $\mu$, which is for convenience.'' }}\]
We say that $\strategy$ is \emph{perfect} if $\omega(G;\strategy)=1$.
\end{definition}

@@

\begin{definition}[Linear code]
For $q$ a prime power and $n,k,d$ integer
a $[n,k,d]_q$ linear code is a $k$-dimensional subspace $\code\subseteq \F_q^n$ such that for every $u\in \code$ such that $u\neq 0$, $|u|\geq d$. Equivalently, we think of $\code$ as a linear map $\code:\F_q^k\to \F_q^n$. We write $E_\code \in \F_q^{k\times n}$ \hnote{this notation might be confusing, especially since we use $G$ and $G_{\code,M}$ for games... maybe call it $E_\code$?}\tnote{ok} for the generator matrix defined by $ E_\code^T e_i =\code(e_i)$ \hnote{what is $\code(e_i)$? I think we should just say that the range of $G_\code^T$ is $\code$}\tnote{It's defined a bit above, ``we think of $\code$ as a linear map...''} for all $i\in\{1,\ldots,k\}$, where $\{e_1,\ldots,e_k\}$ is the standard basis of $\F_q^k$. 
\end{definition}

@@

\begin{definition}[Local tester]\label{def:code-test}
Let $\code$ be an $[n,k,d]_q$ linear code, $\delta:[0,1]\to[0,1]$, and $r\in \N$.
An \emph{$r$-local $\delta$-tester for $\code$} is a pair $M = ((M_S)_{S \subseteq [n]},\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and for each such subset $M_S:\F_q^S\to\{0,1\}$ is a predicate such that the following hold:
\begin{itemize} 
\item (Completeness:) For any $u\in \code$, $\Pr_{S\sim \nu}( M_S(u_S)=1)=1$.
\item (Soundness:) For any $\eps\geq 0$ and any $u\in \F_q^n$ that is within (Hamming) distance at least  $\eps$ from $\code$, $\Pr_{S\sim\nu}(M_S(u_{|S})=0)\geq \delta(\eps)$.  \hnote{should it be $u_S$ or $u|_S$?}\tnote{What difference do you make between the two? We don't define either, so I'm fine using the one you find most intuitive/correct}
\end{itemize}
\end{definition}

@@

\begin{definition}[$\eps$-local presentation]
Let $\code$ be an $[n,k,d]_q$ linear code and $M$ be an $r$-local tester for $\code$. An \emph{$\eps$-local presentation of $(\code,M)$} is a pair $(\mM,A)$ of a tracial von Neumann algebra $\mM$ and a collection of projective measurements $A = \{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}\}_{i \in S }\subset \mM_\infty$, with $B^{S,i} = \{B^{S,i}_b\}_{b\in \F_q}$, such that 
\begin{itemize}
\item $\sum_{a\in \F^S} M(S,a) \, \prod_{i\in S} B^{S,i}_{a_i}= \Id$ 
\item For any $S$ such that $|S|\leq r$ and $i\in S$, let $A^{S,i}=S^i$. Then the two measurement families $\{A^{S,i}\}_{S, i\in S}$ \hnote{Don't quite understand the subscripting, since $A^i$ only depends on $i$}\tnote{I meant to say that we use the same $A_i$ for all $S$ that contain $i$. I rewrote it more explicitly} and $\{B^{S,i}\}_{S, i\in S}$ are $(\eps,\nu')$-close, where $\nu'((S,i))=\nu(S)1_{i\in S}\frac{1}{|S|}$.
\end{itemize} 
\hnote{question about the name: why ``presentation''? the object here is a pair $(\mM,A)$ which looks syntactically the same as a code representation... should it be ``representation''?}\tnote{Yeah...should we use ``presentation'' for both? This avoids confusion with language from representation theory. I did this above, what do you think?}
\end{definition}

@@

\begin{lemma}\label{lem:l1-l2}
\hnote{$(\eps,\mu)$-closeness needs the measurements to be superscripted by questions}\tnote{fixed}
Let $\{P_a^i\}$ and $\{Q_a^i\}$ be two families of projective measurements that are $(\eps,\mu)$-close. Then 
\begin{equation}\label{eq:l1-l2}
\Es{i\in\mI} \sum_{a\in \mA(i)} \tau\big(|P_a-w^*Q_aw|\big) \,\leq\, \eps+ 2 \sqrt{\eps}\;.
\end{equation}
\end{lemma}

@@

\begin{proof}
If $\eps\geq \frac{1}{2}$ the conclusion is trivial (for a suitably large implicit constant in the $O(\cdot)$ notation in \eqref{eq:pull-back}), so assume $\eps<\frac{1}{2}$. 
Define 
\[\tilde{Q}_a = w^* P_a w  + \frac{1}{|\mA|}\big(\Id_\mM - w^* w\big) \in \mM\;.\]
Then $\{\tilde{Q}_a\}$ is a POVM on $\mM$. Moreover, 
\begin{align*}
\sum_a \tau^\mM \big( \tilde{Q}_a^2 \big) &\geq \sum_a \tau^\mM \big( \big(w^* P_a w \big)^2 \big) \\
&= \sum_a \tau^\mM \big(  w^* P_a w w^*P_a w \big)\\
&= \sum_a \tau^\mM \big(  w^* P_a  P P_a w \big) - \sum_a \tau^\mM \big( w^* P_a  ( P - w w^*) P_a w \big)\\
\intertext{
\hnote{I don't get this next line... how did $\tau_\infty$ show up?}\tnote{By definition, $\mM$ is seen as a sub-algebra of $\mM_\infty$, and $\tau_\infty$ restricted to that sub-algebra is $\tau^\cM$. So, whenever $M\in \mM$, $\tau^\mM(M)=\tau_\infty(\mM)$ is a legal ``shortcut'' in the writing. It's this sentence about the ``corner'' in the prelims...should we add something more explicit? Or explain this line here more, since it's the first time we make the manipulation? }
}
&\geq 1 - \eps -  \tau_\infty\Big(\big( P - w w^*\big)\Big(\sum_a  P_a w w^* P_a\Big)\Big)\\ 
&\geq 1- \eps- \tau_\infty\big( P- w w^*\big)\;,
\end{align*}
where the fourth line uses that $P_aPP_a=P_a$, $\sum_a P_a = \Id_\mN$ and the definition of $\eps$ for the first term, and cyclicity of the trace for the second, and the last uses $\|ww^*\|,\|\sum_a P_a\|_\infty\leq 1$. By assumption, 
\begin{align*}
\tau_\infty\big( P- w w^*\big) \,\leq\, \eps\, \tau_\infty(P)\,\leq \frac{\eps}{1-\eps}\;.
\end{align*}
where the last inequality is because by definition, $\tau^N(P)=1$, thus
\[1-\eps \,\leq\, \tau^\mN(ww^*) \,=\, \frac{\tau_\infty(ww^*)}{\tau_\infty(P)}\,=\, \frac{\tau_\infty(w^*w)}{\tau_\infty(P)}  \,\leq\, \frac{1}{\tau_\infty(P)}\]
since $\tau_\infty(w^* w) = \tau^\mM(w^* w)$ and $w^*w\leq I_\mM$. Overall, 
\[ \sum_a \tau^\mM \big( \tilde{Q}_a^2 \big) \,\geq\, 1-\eps-\frac{\eps}{1-\eps}\,\geq\, 1-3\eps\;.\]
To conclude we apply~\cite[Theorem 1.2]{de2021orthogonalization} to obtain a projective measurement $\{Q_a\}$ on $\mM$ such that 
\begin{equation*}
\sum_a \big\|{Q}_a - \tilde{Q}_a \big\|^2_2 \,=\, 27\eps\;.
\end{equation*}
Finally,
\begin{align*}
\sum_a \big\|{Q}_a - w^*{P}_a w\big\|^2_2 &= \sum_a \Big\|{Q}_a - \tilde{Q}_a  + \frac{1}{|\mA|}\big(I_\mM - w^* w\big) \Big\|^2_2\\
&\leq  \sum_a 2\big\|{Q}_a - \tilde{Q}_a\big\|_2^2  + 2\frac{1}{|\mA|}\big\|I_\mM - w^* w\big\|_2^2 \\
&\leq 54 \eps + 2 \tau^\mM( (I_\mM - w^* w)^2 ) \\
&\leq 54 \eps + 2 \tau^\mM(I_\mM - w^* w ) \\
&\leq 56 \eps\;,
\end{align*}
where the second line is by the triangle inequality, the fourth line is due to the fact that $I_\mM - w^* w$ is positive and has operator norm at most $1$, and the last line is by $\tau^\mM(I_\mM - w^* w ) \leq \eps$.
\end{proof}

@@

\begin{proof}
For any $a\in\F^S_q$ let $\tilde{P}^S_a = \prod_{i\in S} B^{S,i}_{a_i}$ (since the measurements $\{B^{S,i}\}_i$ are pairwise commuting, the order of the product does not matter). Then $\{\tilde{P}^S_a\}_{a\in\F_q^S}$ is a projective measurement such that for any $i\in S$ and $b\in \F_q$, 
\[ \sum_{a\,:\, a_i=b} \tilde{P}^S_a \,=\, B^{S,i}_b\;.\]
Using this identity, \hnote{I don't get what's happening in these next few lines... what happened to the product over $B^{S,i}_{a_i}$ in the first line?}\tnote{I added the preceding centered equation to explain, is it ok?}
\begin{align}
\Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big(  (w^S)^* \tilde{P}^S_a w^S \, A^i_{a_i}\big) 
&= \Es{S\sim \nu} \Es{i\in S} \sum_{b\in \F_q}\tau\big(  (w^S)^* B^{S,i}_b w^S\, A^i_{b}\big)\notag \\
&= \Es{S\sim \nu} \Es{i\in S} \frac{1}{2}\Big(\tau\big((w^S)^*w^S\big) + \tau(1) - \sum_{b\in \F_q} \big\|  (w^S)^* B^{S,i}_b w^S - A^i_{b}\big\|_2^2\Big) \notag\\
&\geq \,\frac{1}{2}(1-\eps+1-\eps)\;.\label{eq:s-g-1}
\end{align}
Starting from the $\{\tilde{P}^S_a\}$, let $\{P^S_a\}$ be the family of projective measurements on $\mM$ that is promised by Lemma~\ref{lem:pull-back}. By a simple averaging argument,
\begin{equation}\label{eq:s-g-1b}
\Es{S\sim \nu}\sum_{a\in \F_q^S} \big\| P^S_a - (w^S)^* \tilde{P}^S_a (w^S)\big\|_2^2 \,=\, O(\eps)\;. 
\end{equation}
We can write
\begin{align}
\Big|\Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big( P^S_a A^i_{a_i}\big)
&- \Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big( (w^S)^* \tilde{P}^S_a (w^S)A^i_{a_i}\big)\Big|\notag\\
&= \Big| \Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big(\big(P^S_a - (w^S)^* \tilde{P}^S_a (w^S)\big)A^i_{a_i}\big)\Big|\notag\\
&\leq \Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big(\big|(w^S)^* \tilde{P}^S_a (w^S)-P^S_a\big|\big)\notag\\
&= O(\sqrt{\eps})\;,\label{eq:s-g-2}
\end{align}
where the inequality uses H\"{o}lder's inequality with $\|A^i_a\|\leq 1$ and the last line is by Lemma~\ref{lem:l1-l2} and~\eqref{eq:s-g-1b}.
Using the definition of $G_{\code,M}$, we have shown that \hnote{I think this part requires a little more explanation...for example this is the first time the decision predicate $D(S,i,a,b)$ has shown up in this proof.}\tnote{added a couple lines}
\begin{align*}
 \sum_{S,i} \mu(S,i) \sum_{a\in \F^S_q}\sum_{b\in\F_q} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big)
&=  \Es{S\sim\nu} \Es{i\in S} \sum_{a\in \F^S_q}  \tau\big(  P^S_a  A^i_{a_i}\big)\\
&\geq O\big(\sqrt{\eps}\big) - \Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big( (w^S)^* \tilde{P}^S_a (w^S)A^i_{a_i}\big)\\
&= 1-O\big(\sqrt{\eps}\big)\;,
\end{align*}
where the first line uses the definition of $\mu(\cdot,\cdot)$, the second line uses~\eqref{eq:s-g-2} and the last uses~\eqref{eq:s-g-1}. 
\end{proof}

Claim~\ref{claim:sound-game-1} shows that $\omega(G_{\code,M};\strategy)\geq 1-\eps'$ for $\strategy$ the strategy with measurements $\{A^i_b\}$ and $\{P^{S}_a\}$ and some $\eps'=O(\sqrt{\eps})$. Using the definition of robustness we deduce that $(\mM,A,P)$ \hnote{what is this triple?}\tnote{$A$ and $P$ are defined just above. $C$ and $Q$ are any other measurements. You think we should introduce specific notation?} is $(\delta'(\eps'),\nu)$-close to a perfect strategy $(\mN,C,Q)$ \hnote{same question} for $G_{\code,M}$. Since $\nu$ is uniform on $\{1,\ldots,n\}$ we specialize to the $A$ measurements; using the definition of closeness there exists a projection $P\in \mM_\infty$ such that $\{C^i\}_a \subseteq P\mM_\infty P$ and $\Es{i}\sum_a \|A^i_a-w^* C^i_a w \|_2^2 \leq 2\delta'$, and moreover $\{C^i_a\}$ satisfy that for any $S$ in the support of $\mu$, $\{C^i_a\}$ pairwise commute for $i\in S$. Using the assumption that $(\code,M)$ is Abelian, all the $\{C^i_a\}$ commute and form a representation of $\code$.

@@

\begin{definition}
Let $k\in \N$ and $\delta:[0,1]\to\R_+$. 
A \emph{$(k,\delta(\eps))$-qubit test} is a synchronous game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \field^k$ \tnote{adding:}that are both generating sets and an injection $\phi:(\{X\}\times S_X) \cup (\{Z\}\times S_Z) \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\field$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
\begin{itemize}
\item (Completeness:) There is a synchronous strategy $(\mM,P)$ for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P}^{\phi({W},a)} = \sigma^W(a)$ for every $W\in\{X,Z\}$ and $a\in S_W$. \hnote{What does $\widehat{P}$ refer to here? Is it the observable corresponding to a projective measurement $P$ for question $\phi(W,a)$ that's part of the synchronous strategy?}\tnote{yes}
\item (Soundness:) \tnote{added:}Let $\mu'$ denote the (renormalized) restriction of (the marginal of) $\mu$ to the image of $\phi$ in $\mX$.
Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $(\delta(\eps),\tilde{\mu})$-close \hnote{in light of the next remark, this should also specify the distribution over which the closeness is measured?}\tnote{added} to a strategy on some algebra $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ where $(\mN,\tau')$ is a tracial sub-algebra of $\mM_\infty$ and such that
\[\widehat{P}^{\phi({W},a)} = \sigma^W(a)\otimes \Id_\mN\;.\]
\hnote{Technically, for this to adhere to the definition of closeness, the ``bigger'' algebra needs to be a subalgebra of $\mM_\infty$. Is this obvious?}\tnote{added}
\end{itemize}
\end{definition}

@@

\hnote{is this the ``right'' name? I thought Pauli braiding test was the large question version.}\tnote{Well actually it's ``Pauli basis test'' which is the version from NW. Here, it's closer to the ``quantum low-degree test,'' but it's more general. Technically ``Pauli braiding'' is introduced in the paper by Anand and I on the quantum linearity test, which at least has the merit of falling in the class of tests considered here. So we could say that and explain why we now use the name ``Pauli braiding'' for a more general class. Would that be ok?}

>>>>

When we write $\Es{i\in \mX}$ where $\mX$ is a finite set, we mean the expectation over $i$ chosen uniformly at random from $\mX$, i.e.\ $\frac{1}{|\mX|} \sum_{i\in \mX}$. \hnote{added:} For a vector $u \in \mX^n$ and a subset $S \subseteq [n]$, we write $u_S$ to denote the vector in $\mX^S$ which is the restriction of $u$ to $S$.

@@

\hnote{remove this?} We end with a couple lemma that will prove useful.

@@

\begin{definition}[Synchronous strategy]
If $G=(\mX,\mu,\mA,D)$ is a game and $(\mM,\tau)$ a tracial von Neumann algebra, a \emph{synchronous strategy $\strategy$ for $G$ on $(\mM,\tau)$} is, for every $x\in \mX$, a projective measurement $(P^x_a)_{a\in \mA(x)}$ on $\mM$. The value of a strategy $\strategy$ in $G$ is 
\[ \omega(G;\strategy)\,=\, \sum_{(x,y)\in\mX\times\mX}\frac{1}{2}\big(\mu(x,y)+\mu(y,x)\big) \sum_{(a,b)\in\mA(x)\times\mA(y)} D(x,y,a,b)\, \tau\big(P^x_a \,P^y_b\big) \;.\footnote{Note the symmetrization of $\mu$. This is to avoid explicitly requiring $\mu$ to be permutation-invariant in the definition of a game.}\]
We say that $\strategy$ is \emph{perfect} if $\omega(G;\strategy)=1$.
\end{definition}

@@

\begin{definition}[Linear code]
For $q$ a prime power and $n,k,d$ integer
a $[n,k,d]_q$ linear code is a $k$-dimensional subspace $\code\subseteq \F_q^n$ such that for every $u\in \code$ such that $u\neq 0$, $|u|\geq d$. Equivalently, we think of $\code$ as a linear map $\code:\F_q^k\to \F_q^n$. We write $E_\code \in \F_q^{k\times n}$ for the generator matrix defined by $ E_\code^T e_i =\code(e_i)$ for all $i\in\{1,\ldots,k\}$, where $\{e_1,\ldots,e_k\}$ is the standard basis of $\F_q^k$. 
\end{definition}

@@

\begin{definition}[Local tester]\label{def:code-test}
Let $\code$ be an $[n,k,d]_q$ linear code, $\delta:[0,1]\to[0,1]$, and $r\in \N$.
An \emph{$r$-local $\delta$-tester for $\code$} is a pair $M = ((M_S)_{S \subseteq [n]},\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and for each such subset $M_S:\F_q^S\to\{0,1\}$ is a predicate such that the following hold:
\begin{itemize} 
\item (Completeness:) For any $u\in \code$, $\Pr_{S\sim \nu}( M_S(u_S)=1)=1$.
\item (Soundness:) For any $\eps\geq 0$ and any $u\in \F_q^n$ that is within (Hamming) distance at least  $\eps$ from $\code$, $\Pr_{S\sim\nu}(M_S(u_{|S})=0)\geq \delta(\eps)$.  \hnote{should it be $u_S$ or $u|_S$?}\tnote{What difference do you make between the two? We don't define either, so I'm fine using the one you find most intuitive/correct}\hnote{$u_S$ is fine by me (and we should say what this means in the preliminaries), I just saw both and thought we should be consistent.}
\end{itemize}
\end{definition}

@@

\begin{definition}[$\eps$-local presentation]
Let $\code$ be an $[n,k,d]_q$ linear code and $M$ be an $r$-local tester for $\code$. An \emph{$\eps$-local presentation of $(\code,M)$} is a pair $(\mM,A)$ of a tracial von Neumann algebra $\mM$ and a collection of projective measurements $A = \{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}\}_{i \in S }\subset \mM_\infty$, with $B^{S,i} = \{B^{S,i}_b\}_{b\in \F_q}$, such that 
\begin{itemize}
\item $\sum_{a\in \F^S} M(S,a) \, \prod_{i\in S} B^{S,i}_{a_i}= \Id$ 
\item For any $S$ such that $|S|\leq r$ and $i\in S$, let $A^{S,i}=S^i$. Then the two measurement families $\{A^{S,i}\}_{S, i\in S}$ and $\{B^{S,i}\}_{S, i\in S}$ are $(\eps,\nu')$-close, where $\nu'((S,i))=\nu(S)1_{i\in S}\frac{1}{|S|}$.
\end{itemize} 
\hnote{question about the name: why ``presentation''? the object here is a pair $(\mM,A)$ which looks syntactically the same as a code representation... should it be ``representation''?}\tnote{Yeah...should we use ``presentation'' for both? This avoids confusion with language from representation theory. I did this above, what do you think?}\hnote{I actually like the term representation for its allusion to representation theory. But we should be consistent with both; you pick.}
\end{definition}

@@

\begin{lemma}\label{lem:l1-l2}
Let $\{P_a^i\}$ and $\{Q_a^i\}$ be two families of projective measurements that are $(\eps,\mu)$-close. Then 
\begin{equation}\label{eq:l1-l2}
\Es{i\in\mI} \sum_{a\in \mA(i)} \tau\big(|P_a-w^*Q_aw|\big) \,\leq\, \eps+ 2 \sqrt{\eps}\;.
\end{equation}
\end{lemma}

@@

\begin{proof}
If $\eps\geq \frac{1}{2}$ the conclusion is trivial (for a suitably large implicit constant in the $O(\cdot)$ notation in \eqref{eq:pull-back}), so assume $\eps<\frac{1}{2}$. 
Define 
\[\tilde{Q}_a = w^* P_a w  + \frac{1}{|\mA|}\big(\Id_\mM - w^* w\big) \in \mM\;.\]
Then $\{\tilde{Q}_a\}$ is a POVM on $\mM$. Moreover, 
\begin{align*}
\sum_a \tau^\mM \big( \tilde{Q}_a^2 \big) &\geq \sum_a \tau^\mM \big( \big(w^* P_a w \big)^2 \big) \\
&= \sum_a \tau^\mM \big(  w^* P_a w w^*P_a w \big)\\
&= \sum_a \tau^\mM \big(  w^* P_a  P P_a w \big) - \sum_a \tau^\mM \big( w^* P_a  ( P - w w^*) P_a w \big)\\
\intertext{
\hnote{I don't get this next line... how did $\tau_\infty$ show up?}\tnote{By definition, $\mM$ is seen as a sub-algebra of $\mM_\infty$, and $\tau_\infty$ restricted to that sub-algebra is $\tau^\cM$. So, whenever $M\in \mM$, $\tau^\mM(M)=\tau_\infty(\mM)$ is a legal ``shortcut'' in the writing. It's this sentence about the ``corner'' in the prelims...should we add something more explicit? Or explain this line here more, since it's the first time we make the manipulation? }\hnote{I think it would be good to add at least one line of explanation...}
}
&\geq 1 - \eps -  \tau_\infty\Big(\big( P - w w^*\big)\Big(\sum_a  P_a w w^* P_a\Big)\Big)\\ 
&\geq 1- \eps- \tau_\infty\big( P- w w^*\big)\;,
\end{align*}
where the fourth line uses that $P_aPP_a=P_a$, $\sum_a P_a = \Id_\mN$ and the definition of $\eps$ for the first term, and cyclicity of the trace for the second, and the last uses $\|ww^*\|,\|\sum_a P_a\|_\infty\leq 1$. By assumption, 
\begin{align*}
\tau_\infty\big( P- w w^*\big) \,\leq\, \eps\, \tau_\infty(P)\,\leq \frac{\eps}{1-\eps}\;.
\end{align*}
where the last inequality is because by definition, $\tau^N(P)=1$, thus
\[1-\eps \,\leq\, \tau^\mN(ww^*) \,=\, \frac{\tau_\infty(ww^*)}{\tau_\infty(P)}\,=\, \frac{\tau_\infty(w^*w)}{\tau_\infty(P)}  \,\leq\, \frac{1}{\tau_\infty(P)}\]
since $\tau_\infty(w^* w) = \tau^\mM(w^* w)$ and $w^*w\leq I_\mM$. Overall, 
\[ \sum_a \tau^\mM \big( \tilde{Q}_a^2 \big) \,\geq\, 1-\eps-\frac{\eps}{1-\eps}\,\geq\, 1-3\eps\;.\]
To conclude we apply~\cite[Theorem 1.2]{de2021orthogonalization} to obtain a projective measurement $\{Q_a\}$ on $\mM$ such that 
\begin{equation*}
\sum_a \big\|{Q}_a - \tilde{Q}_a \big\|^2_2 \,=\, 27\eps\;.
\end{equation*}
Finally,
\begin{align*}
\sum_a \big\|{Q}_a - w^*{P}_a w\big\|^2_2 &= \sum_a \Big\|{Q}_a - \tilde{Q}_a  + \frac{1}{|\mA|}\big(I_\mM - w^* w\big) \Big\|^2_2\\
&\leq  \sum_a 2\big\|{Q}_a - \tilde{Q}_a\big\|_2^2  + 2\frac{1}{|\mA|}\big\|I_\mM - w^* w\big\|_2^2 \\
&\leq 54 \eps + 2 \tau^\mM( (I_\mM - w^* w)^2 ) \\
&\leq 54 \eps + 2 \tau^\mM(I_\mM - w^* w ) \\
&\leq 56 \eps\;,
\end{align*}
where the second line is by the triangle inequality, the fourth line is due to the fact that $I_\mM - w^* w$ is positive and has operator norm at most $1$, and the last line is by $\tau^\mM(I_\mM - w^* w ) \leq \eps$.
\end{proof}

@@

\begin{proof}
For any $a\in\F^S_q$ let $\tilde{P}^S_a = \prod_{i\in S} B^{S,i}_{a_i}$ (since the measurements $\{B^{S,i}\}_i$ are pairwise commuting, the order of the product does not matter). Then $\{\tilde{P}^S_a\}_{a\in\F_q^S}$ is a projective measurement such that for any $i\in S$ and $b\in \F_q$, 
\[ \sum_{a\,:\, a_i=b} \tilde{P}^S_a \,=\, B^{S,i}_b\;.\]
Using this identity,
\begin{align}
\Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big(  (w^S)^* \tilde{P}^S_a w^S \, A^i_{a_i}\big) 
&= \Es{S\sim \nu} \Es{i\in S} \sum_{b\in \F_q}\tau\big(  (w^S)^* B^{S,i}_b w^S\, A^i_{b}\big)\notag \\
&= \Es{S\sim \nu} \Es{i\in S} \frac{1}{2}\Big(\tau\big((w^S)^*w^S\big) + \tau(1) - \sum_{b\in \F_q} \big\|  (w^S)^* B^{S,i}_b w^S - A^i_{b}\big\|_2^2\Big) \notag\\
&\geq \,\frac{1}{2}(1-\eps+1-\eps)\;.\label{eq:s-g-1}
\end{align}
Starting from the $\{\tilde{P}^S_a\}$, let $\{P^S_a\}$ be the family of projective measurements on $\mM$ that is promised by Lemma~\ref{lem:pull-back}. By a simple averaging argument,
\begin{equation}\label{eq:s-g-1b}
\Es{S\sim \nu}\sum_{a\in \F_q^S} \big\| P^S_a - (w^S)^* \tilde{P}^S_a (w^S)\big\|_2^2 \,=\, O(\eps)\;. 
\end{equation}
We can write
\begin{align}
\Big|\Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big( P^S_a A^i_{a_i}\big)
&- \Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big( (w^S)^* \tilde{P}^S_a (w^S)A^i_{a_i}\big)\Big|\notag\\
&= \Big| \Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big(\big(P^S_a - (w^S)^* \tilde{P}^S_a (w^S)\big)A^i_{a_i}\big)\Big|\notag\\
&\leq \Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big(\big|(w^S)^* \tilde{P}^S_a (w^S)-P^S_a\big|\big)\notag\\
&= O(\sqrt{\eps})\;,\label{eq:s-g-2}
\end{align}
where the inequality uses H\"{o}lder's inequality with $\|A^i_a\|\leq 1$ and the last line is by Lemma~\ref{lem:l1-l2} and~\eqref{eq:s-g-1b}.
Using the definition of $G_{\code,M}$, we have shown that
\begin{align*}
 \sum_{S,i} \mu(S,i) \sum_{a\in \F^S_q}\sum_{b\in\F_q} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big)
&=  \Es{S\sim\nu} \Es{i\in S} \sum_{a\in \F^S_q}  \tau\big(  P^S_a  A^i_{a_i}\big)\\
&\geq O\big(\sqrt{\eps}\big) - \Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big( (w^S)^* \tilde{P}^S_a (w^S)A^i_{a_i}\big)\\
&= 1-O\big(\sqrt{\eps}\big)\;,
\end{align*}
where the first line uses the definition of $\mu(\cdot,\cdot)$, the second line uses~\eqref{eq:s-g-2} and the last uses~\eqref{eq:s-g-1}. 
\end{proof}

Claim~\ref{claim:sound-game-1} shows that $\omega(G_{\code,M};\strategy)\geq 1-\eps'$ for $\strategy$ the strategy with measurements $\{A^i_b\}$ and $\{P^{S}_a\}$ and some $\eps'=O(\sqrt{\eps})$. Using the definition of robustness we deduce that $(\mM,A,P)$ \hnote{what is this triple?}\tnote{$A$ and $P$ are defined just above. $C$ and $Q$ are any other measurements. You think we should introduce specific notation?} \hnote{it's just that the ``triple'' notation for strategies hasn't been introduced... technically the def'n of strategy is an assignment of PVMs to every question. maybe write $\strategy$ instead of $(\mM,A,P)$ and $\strategy'$ instead of $(\mN,C,Q)$?} is $(\delta'(\eps'),\nu)$-close to a perfect strategy $(\mN,C,Q)$ for $G_{\code,M}$. Since $\nu$ is uniform on $\{1,\ldots,n\}$ we specialize to the $A$ measurements; using the definition of closeness there exists a projection $P\in \mM_\infty$ such that $\{C^i\}_a \subseteq P\mM_\infty P$ and $\Es{i}\sum_a \|A^i_a-w^* C^i_a w \|_2^2 \leq 2\delta'$, and moreover $\{C^i_a\}$ satisfy that for any $S$ in the support of $\mu$, $\{C^i_a\}$ pairwise commute for $i\in S$. Using the assumption that $(\code,M)$ is Abelian, all the $\{C^i_a\}$ commute and form a representation of $\code$.

@@

\begin{definition}
Let $k\in \N$ and $\delta:[0,1]\to\R_+$. 
A \emph{$(k,\delta(\eps))$-qubit test} is a synchronous game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \field^k$ \tnote{adding:}that are both generating sets and an injection $\phi:(\{X\}\times S_X) \cup (\{Z\}\times S_Z) \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\field$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
\begin{itemize}
\item (Completeness:) There is a synchronous strategy $(\mM,P)$ for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P}^{\phi({W},a)} = \sigma^W(a)$ for every $W\in\{X,Z\}$ and $a\in S_W$. 
\item (Soundness:) \tnote{added:}Let $\mu'$ denote the (renormalized) restriction of (the marginal of) $\mu$ to the image of $\phi$ in $\mX$.
Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $(\delta(\eps),\tilde{\mu})$-close to a strategy on some algebra $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ where $(\mN,\tau')$ is a tracial sub-algebra of $\mM_\infty$ and such that
\[\widehat{P}^{\phi({W},a)} = \sigma^W(a)\otimes \Id_\mN\;.\]
\end{itemize}
\end{definition}

@@
